
\documentclass[preview,border=0.3pt]{standalone}
% import xcolor if available and not already present
\IfFileExists{xcolor.sty}{\usepackage{xcolor}}{}%
\usepackage{amsmath}
\usepackage{amssymb}
\IfFileExists{latexsym.sty}{\usepackage{latexsym}}{}
\IfFileExists{mathtools.sty}{\usepackage{mathtools}}{}
\usepackage{/home/etienne/ownCloud/Articles et conférences/Articles/2019.08 Ultramicroscopy/2-review-reponse/style/Notation}
\begin{document}
% set the foreground color
\IfFileExists{xcolor.sty}{\color[HTML]{CCCCCC}}{}%
\(
p_L(\mathbf{y}) = \arg\min_\mathbf{x}\left\{ g(\mathbf{x}) + \frac{L}{2}||\mathbf{x} - \left( \underbrace{\mathbf{y} - \frac{1}{L} \nabla f(\mathbf{y}) \right)||^2 \right\}
\end{equation}

\end{response}


%-----------------------------------------------------------

\begin{question}[Page 14 and 15]
References are not consistent, Sometimes the year is in brackets, sometimes not.
\end{question}

\begin{response}

\end{response}


%-----------------------------------------------------------

\begin{question}[General]
The authors should revise the manuscripts in terms of english language. There are a lot of typos, misspellings and grammatical errors in the document. This will facilitate reading and understanding.
\end{question}

\begin{response}

\end{response}


%-----------------------------------------------------------

\begin{question}[General]
The structure of Section 4 could be enhanced. It should be clearer differentiated between data, data processing, experiments, results, and discussion. In the current version there is no real red thread, which made reading und following more difficult than needed.
\end{question}

\begin{response}

\end{response}


%-----------------------------------------------------------

\begin{question}[General]
Some formulation are quite subjective and should be reformulated. Examples are "much more accurate", "quite bad" or "prohibitive computation".
\end{question}

\begin{response}
Thanks for pointing these typos that have been corrected in the manuscript.

\mdbox{
\begin{itemize}
    \item \emph{much more accurate} has been modified into \corr{more accurate},
    \item \emph{quite bad} has been modified into \corr{bad},
    \item \emph{prohibitive computation} has been modified into \corr{}.
\end{itemize}
}
\end{response}


%-----------------------------------------------------------
\)
\end{document}
